Insecticide resistance evolution with mixtures and sequences : a model-based graphical introduction and summary

### 2017-04-24 inst/documents/paper2/paper2_resistance_mechanisms_mixtures.Rmd
paper writing

@@

>>>>

_comments from Hilary_
_This would seem to be a critical point to stress - with examples of how this might be acheived._

_Limitations that haven't been addressed is the possiblility that resistance is poylgenic, and the possibility of cross resistance (e.g a P450 may cause partial resistance to both)._

_Something further to guide readers on how they might determine dominance would also be useful given how crucial this is._

@@

# add side panels for labels
layout( matrix(c(1:6,0,7,7,0,8,9),4,3, byrow = TRUE), heights=c(1,1,0.15,0.2), widths=c(0.1,1,1) )
#layout.show(n=9)
